%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  ICAR2003_2e.tex  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper]{ICAR2003}

\begin{document} 

% create the title header:

\title{\Large\bf My Wonderful Article in IEEE Format for ICAR 2003}
\author{\begin{tabular}{cc}
%\affiliation{\begin{tabular}{cc}
\bf I.M.Author	& \bf M.Y. Coauthor \\
 & \\
My Department	& Coauthor Department \\
My Institute	& Coauthor Institute \\
My Address	& Coauthor Address \\
My e-mail	& Coauthor e-mail \\
\end{tabular}}
\date{}

\maketitle

\thispagestyle{empty}

\begin{Abstract}
This is the abstract of my paper.
It must fit within the size allowed, which is about 3 inches, including section title, which is 11 point bold font.
If you don't want the text in italics, simply remove the 'em' command and the curly braces which bound the abstract text.
If you have em commands within an italicized abstract, the text will come out as normal (nonitalicized) text.
\end{Abstract} 

\section{Introduction}
Here is my introduction text.
There are 2 blank lines before the section heading and one afterwards.
Heading text is 12 point bold font.
Paragraphs are not indented.
I may want a numbered subsection, which is done as follows.

\subsection{Previous Work}
In subsections there is 1 blank line before the section heading and one 
afterwards.  Heading text is 11 point bold font.  Paragraphs are separated by 
blank lines without tabs.

Throughout I may cite references of the form \cite{key:foo} or
\cite{foo:baz}, and \LaTeX\ will keep track of numbering.  The numbers are based
on the order you place them in the bibliography, not the order they appear in
the text.  They should (I believe) be in alphabetical order.  \LaTeX\ will put
square brackets about the number within the text of your paper.  For those of 
you new to the bibliography package, you may have to run the \LaTeX\ process 
twice to allow all references to be resolved.  You will get a warning about
a missing .aux file.  Just rerun \LaTeX\ and it will be ok.


\section{Summary and Conclusions}
This template will get you through the minimum article, i.e., no figures or
equations.  To include those, please refer to your \LaTeX\ manual and the IEEE
publications guidelines.  Good Luck!

Here is a simple example of doing equations.
The \LaTeX\ automatically increments the equation number.
\begin{equation}
y = x + 1
\label{eq.1}  %this is for automatic referencing
\end{equation}
Squaring Eq. (\ref{eq.1}), we obtain 
\begin{equation}
y^2 = (x + 1)^2 = x^2 + 2x +1
\label{eq.2}
\end{equation}

%this is how to do an unnumbered subsection

\begin{Acknowledgment}
This is how to do an unnumbered subsection, which comes out in 11 point bold
font.  Here I thank my colleagues, especially Mike Gennert, who know more 
about Tex and \LaTeX\ than I.
\end{Acknowledgment}

\begin{thebibliography}{9}
\bibitem{key:foo}
I. M. Author, 
``Some Related Article I Wrote,''
{\em Some Fine Journal}, Vol. 17, pp. 1-100, 1987.

\bibitem{foo:baz}
A. N. Expert, 
{\em A Book He Wrote,}
His Publisher, 1989.
\end{thebibliography}

\end{document}

