\subsection*{Synopsis}
ACTS is a fast color segmentation system written by Paul Rybski and sold
by ActivMedia; see:\\
\indent {\tt http://www.activrobots.com}\\
After training, ACTS finds colored blobs in a single camera image.
Player's {\tt acts} driver provides access to ACTS.


\subsection*{Interfaces}

\noindent Supported interfaces:
\begin{itemize}
\item {\tt blobfinder}
\end{itemize}

\noindent Required devices:
\begin{itemize}
\item None.
\end{itemize}

\noindent Supported configuration requests:
\begin{itemize}
\item None.
\end{itemize}


\subsection*{Configuration file options}
Note: In the table below, a default value of (none) indicates that the
associated option will not be passed to ACTS.  As a result, ACTS's own
internal default for that parameter will be used.  Consult the ACTS manual
to determine what those defaults are.

\begin{center}
{\small \begin{tabularx}{\columnwidth}{|l|l|c|X|}
\hline
Name & Type & Default & Meaning\\
\hline
{\tt path} & string & {\tt ""} & Path to the ACTS executable (leave empty to
search the user's PATH for {\tt acts}).\\

{\tt configfile} & string & {\tt "/usr/local/acts/actsconfig"} & Path to the
ACTS configuration file to be used.\\

{\tt version} & string & {\tt "2.0"} & The version of ACTS in use (should be
{\tt "1.0"}, {\tt "1.2"}, or {\tt "2.0"}).\\

{\tt width} & integer & {\tt 160} & Width of the camera image (in pixels).\\

{\tt height} & integer & {\tt 120} & Height of the camera image (in pixels).\\

{\tt pixels} & integer & (none) & Minimum area required to call a blob a blob 
(in pixels).\\

{\tt port} & integer & {\tt 5001} & TCP port by which Player should connect to
ACTS.\\

{\tt fps} & integer & (none) & Frame per second of the camera.\\

{\tt drivertype} & string & (none) & Type of framegrabber driver in use (e.g.,
{\tt "bttv"}, {\tt "bt848"}, {\tt "matrox"}).\\

{\tt invert} & integer & (none) & Is the camera inverted?\\

{\tt devicepath} & string & (none) & Path to the device file for the
framegrabber (e.g., {\tt "/dev/fg0"}).\\

{\tt channel} & integer & (none) & Which channel to select on the
framegrabber.\\

{\tt norm} & string & (none) & Normalization??\\

{\tt pxc200} & integer & (none) & Is the framegrabber a PXC200?\\

{\tt brightness} & float & (none) & Brightness level??\\

{\tt contrast} & float & (none) & Contrast level??\\
\hline
\end{tabularx}}
\end{center}

\subsection*{Notes}

\begin{itemize}
\item The {\tt acts} driver supports ACTS versions 1.0, 1.2, and 2.0.
\item PXC200 framegrabbers, when accessed through the {\tt bttv} module,
may cause the machine to hang.  A workaround is to first read a frame from
a framegrabber channel on which there is no video signal, and then start
reading from the right channel.  (This problem is unrelated to Player's {\tt
acts} driver)
\end{itemize}
