\subsection*{Synopsis}
The {\tt nomad} driver connects over a serial port to a Nomad 200
robot running Nomadics' ``robotd'' daemon.   Data and commands are handled
via the custom {\tt nomad} interface.

The {\tt nomad\_position} and {\tt nomad\_sonar} drivers provide data in
the standard position and sonar interfaces.  Position interface provides
data, takes commands and supports geometry config.  Sonar interface
provides data and supports geometry config. This driver is rudimentary
but tested and working on the Nomad 200. It may also work on other Nomads
that run robotd.

\subsection*{Interfaces}

\noindent Supported interfaces:
\begin{itemize}
\item {\tt nomad}
\item {\tt position}
\item {\tt sonar}
\end{itemize}

\noindent Required devices:
\begin{itemize}
\item None.
\end{itemize}

\noindent Supported configuration requests:
\begin{itemize}
\item {\tt GET\_GEOM} (position and sonar)
\end{itemize}

\subsection*{Configuration file options}

\noindent {\tt nomad}:\\
\begin{center}
{\small \begin{tabularx}{\columnwidth}{|l|l|c|X|}
\hline
Name & Type & Default & Meaning\\
\hline
{\tt serial\_device} & string & {\tt ""} & The serial port to be used\\
{\tt serial\_speed} & int & {\tt -1} & The baud rate to use \\
\hline
\end{tabularx}}
\end{center}

\noindent {\tt nomad\_position}:\\
\begin{center}
{\small \begin{tabularx}{\columnwidth}{|l|l|c|X|}
\hline
Name & Type & Default & Meaning\\
\hline
{\tt nomad\_index} & int & {\tt 0} & The index of the underlying nomad
device.\\
\hline
\end{tabularx}}
\end{center}

\noindent {\tt nomad\_sonar}:\\
\begin{center}
{\small \begin{tabularx}{\columnwidth}{|l|l|c|X|}
\hline
Name & Type & Default & Meaning\\
\hline
{\tt nomad\_index} & int & {\tt 0} & The index of the underlying nomad
device.\\
\hline
\end{tabularx}}
\end{center}

\subsection*{Notes}
