\subsection*{Synopsis}
Many robots made by ActivMedia, such as the Pioneer series and the AmigoBot,
are controlled by a microcontroller that runs a special embedded operating
system called P2OS (on older robots it is called PSOS).  The host computer
talks to the P2OS microcontroller over a standard RS232 serial line.  Player
includes a driver that offer access to the various P2OS-mediated devices,
logically splitting up the devices' functionality.

\subsection*{Interfaces / Configuration requests}
Although all the P2OS interaction is actually done in a single thread, the
different P2OS devices are accessed through different Player drivers, each
supporting a different interface and supporting some subset of configuration
requests:
\begin{itemize}
\item {\tt p2os\_aio}:
  \begin{itemize}
  \item Interface: {\tt aio} (see Section~\ref{sect:aio})
  \item Configurations: none
  \item Notes: Provides access to analog User I/O.
  \end{itemize}
\item {\tt p2os\_bumper}:
  \begin{itemize}
  \item Interface: {\tt bumper} (see Section~\ref{sect:bumper})
  \item Configurations: none
  \item Notes: Provides access to Pioneer bumpers, for those robots so equipped.
  \end{itemize}
\item {\tt p2os\_cmucam}:
  \begin{itemize}
  \item Interface: {\tt blobfinder} (see Section~\ref{sect:blobfinder})
  \item Configurations: {\tt SET\_COLOR}, {\tt SET\_IMAGER\_PARAMS}
  \item Notes: Controls a CMUCam that is connected to the AUX2 port on the
               P2OS board.  Use the {\tt SET\_COLOR} request to tell the
               camera which color to track.
  \end{itemize}
\item {\tt p2os\_compass}:
  \begin{itemize}
  \item Interface: {\tt position} (see Section~\ref{sect:position})
  \item Configurations: none
  \item Notes: Fills the compass heading into the {\tt yaw} field of the {\tt
  position} data packet.  Accepts no commands.
  \end{itemize}
\item {\tt p2os\_dio}:
  \begin{itemize}
  \item Interface: {\tt dio} (see Section~\ref{sect:dio})
  \item Configurations: none
  \item Notes: Provides access to digital User I/O.
  \end{itemize}
\item {\tt p2os\_gripper}:
  \begin{itemize}
  \item Interface: {\tt gripper} (see Section~\ref{sect:gripper})
  \item Configurations: none
  \item Notes: Provides access to a Pioneer gripper, for those robots so
        equipped.
  \end{itemize}
\item {\tt p2os\_position}:
  \begin{itemize}
  \item Interface: {\tt position} (see Section~\ref{sect:position})
  \item Configurations: {\tt GET\_GEOM}, {\tt MOTOR\_POWER}, {\tt
  VELOCITY\_MODE}, {\tt RESET\_ODOM}
  \item Notes: Provides access to a differential wheelbase.  Only speed control 
  is supported.
  \end{itemize}
\item {\tt p2os\_power}:
  \begin{itemize}
  \item Interface: {\tt power} (see Section~\ref{sect:power})
  \item Configurations: none
  \item Notes: Provides access to battery charge information.
  \end{itemize}
\item {\tt p2os\_sonar}:
  \begin{itemize}
  \item Interface: {\tt sonar} (see Section~\ref{sect:sonar})
  \item Configurations: {\tt GET\_GEOM}, {\tt POWER}
  \item Notes: Provides access to a sonar array.  Sonar indices start with 0
  at the front left and increase clockwise.
  \end{itemize}
\item {\tt p2os\_sound}:
  \begin{itemize}
  \item Interface: {\tt sound} (see Section~\ref{sect:sound})
  \item Configurations: none
  \item Notes: Allows you to play pre-recorded sound files on an Amigobot
  (and other robots?).
  \end{itemize}
\end{itemize}

\subsection*{Configuration file options}
The configuration file options listed in Table~\ref{table:p2os_options}
control how Player communicates with P2OS.  Any option can be specified for
any of the drivers listed in the previous section; if an option is specified
for more than one driver, the value given last will be used.

\begin{table}[ht]
\begin{center}
{\small \begin{tabular}{|l|l|c|l|}
\hline
Name & Type & Default & Meaning\\
\hline
{\tt port} & string & {\tt "/dev/ttyS0"} & The serial port to be used\\
\hline
{\tt radio} & integer & {\tt 0} & Nonzero if a radio modem is being used; 
zero for a direct serial link\\
\hline
\end{tabular}}
\end{center}
\caption{{\em Configuration file options for the {\tt p2os\_*} drivers.}}
\label{table:p2os_options}
\end{table}

\subsection*{Notes}
\begin{itemize}
\item The connection to the P2OS microcontroller is only kept open while
at least one client has at least one of the P2OS-mediated devices open.
When the last P2OS device is closed, the connection to P2OS is also closed.
Implications include: odometry is reset to (0,0,0), motors might be turned off.
\item Since the P2OS driver uses static C++ class members, only one P2OS
robot can be controlled by Player at any given time.  If you want to control
more than one P2OS robots, you'll need to run a separate instance of Player
for each.
\item This driver can usually initiate a connection to P2OS even when P2OS was 
not properly shut down last time.  However, if the connection to P2OS is
interrupted (e.g., the serial cable is pulled out), then the driver is not
likely to recover.
\item This driver likely only works in Linux.
\end{itemize}
