
\subsection*{Synopsis}

The {\tt readlog} driver can be used to ``replay'' data stored in a
log file.  This is particularly useful for debugging client programs,
since users may run their clients against the same data set over and
over again.  Suitable log files can be generated using the {\tt
writelog} driver, or they may be downloaded from the Robotics Data Set
Repository (Radish):
  \begin{quote} 
  \RADISHHOMEPAGE 
  \end{quote}
Note that, to make use of log file data, Player must be started in a
special mode:
  \begin{verbatim}
  $ player -r <logfile> <configfile>
  \end{verbatim} %$
The {\tt -r} switch instructs Player to load the given log file, and
replay the data according the configuration specified in
\verb+<configfile>+.  See the below for some usage examples of the 
{\tt readlog} driver.



\subsection*{Interfaces}

The {\tt readlog} driver currently supports the following interfaces:
{\tt laser}, {\tt position}, {\tt wifi}.


\subsection*{Configuration file options}

\begin{center}
{\small \begin{tabularx}{\columnwidth}{|l|l|c|X|}
\hline
Name & Type & Default & Meaning\\
\hline
{\tt index} & integer & 0 & Device index in the log file. \\
\hline
\end{tabularx}}
\end{center}

%\subsection*{Notes}



\subsection*{Example: Replay Odometry and Laser Data}

The following configuration file {\tt foo.cfg} will read odometry and
laser data from a log file:
  \begin{verbatim}
  position:0 (driver "readlog" index 0)
  laser:0 (driver "readlog" index 0)
  \end{verbatim}
The Player server must also be started in the appropriate mode:
  \begin{verbatim}
  $ player -r foo.log foo.cfg
  \end{verbatim} %$
where {\tt foo.log} contains the data to be replayed.  See Section
\ref{sect:writelog_driver} for an example that shows how to generate a
suitable log file using the {\tt writelog} driver.


\subsection*{Example: Post-hoc Localization}

A particularly useful feature of the {\tt readlog} driver is that it
can be used to generate localization information a robot the {\em
after} the experiment has been performed.  The following configuration
file {\tt bar.cfg} will read odometry and laser data from a log file,
and pass it to the {\tt amcl} driver to generate robot pose estimates.
  \begin{verbatim}
  position:0 (driver "readlog" index 0)
  laser:0 (driver "readlog" index 0)
  localize:0 
  (
    driver "amcl" 
    position_index 0 
    laser_index 0 
    map_file "mymap.pnm" 
    map_scale 0.05
  )
  \end{verbatim}
The Player server must also be started in the appropriate mode:
  \begin{verbatim}
  $ player -r foo.log bar.cfg
  \end{verbatim} %$


