\subsection*{Synopsis}
The {\tt rwi\_*} family of drivers are used to control RWI robots using
RWI's Mobility software.  To date, these drivers have been tested on the
B21r, but they {\em should} work with other Mobility-controlled robots.

\note{This documentation may be incomplete and/or wrong, because I (brian) 
didn't write the driver.  Comments and corrections from users are welcome.}

\subsection*{Interfaces / Configuration requests}
Although all the Mobility interaction is actually done in a single thread, the
different Mobility devices are accessed through different Player drivers, each
supporting a different interface and supporting some subset of configuration
requests:
\begin{itemize}
\item {\tt rwi\_bumper}:
  \begin{itemize}
  \item Interface: {\tt bumper} (see Section~\ref{sect:bumper})
  \item Configurations: none
  \item Notes: Provides access to RWI bumpers, for those robots so equipped.
  \end{itemize}
\item {\tt rwi\_laser}:
  \begin{itemize}
  \item Interface: {\tt laser} (see Section~\ref{sect:laser})
  \item Configurations: none
  \item Notes: Provides access to Mobility-controlled laser range-finder, for 
        those robots so equipped.
  \end{itemize}
\item {\tt rwi\_position}:
  \begin{itemize}
  \item Interface: {\tt position} (see Section~\ref{sect:position})
  \item Configurations: {\tt GET\_GEOM}, {\tt MOTOR\_POWER}, {\tt RESET\_ODOM}
  \item Notes: Provides access to a synchro-drive wheelbase.  
               Only speed control is supported.
  \end{itemize}
\item {\tt rwi\_power}:
  \begin{itemize}
  \item Interface: {\tt power} (see Section~\ref{sect:power})
  \item Configurations: none
  \item Notes: Provides access to battery charge information.
  \end{itemize}
\item {\tt rwi\_sonar}:
  \begin{itemize}
  \item Interface: {\tt sonar} (see Section~\ref{sect:sonar})
  \item Configurations: {\tt GET\_GEOM}, {\tt POWER}
  \item Notes: Provides access to a sonar array.
  \end{itemize}
\end{itemize}

\subsection*{Configuration file options}
\begin{center}
{\small \begin{tabular}{|l|l|c|l|}
\hline
Name & Type & Default & Meaning\\
\hline
{\tt name} & string & {\tt "B21R"} & The name of the robot to which Player
should connect\\
\hline
\end{tabular}}
\end{center}

