
\subsection*{Synopsis}

The {\tt writelog} driver can be used to store data from other devices
within the Player server.  The log files generated in this way can be
``replayed'' using the {\tt readlog} driver.  See the below for some
usage examples of the {\tt writelog} driver.



\subsection*{Interfaces}

The {\tt writelog} driver currently supports the {\tt null} interface,
meaning that it generates no data, and accepts no commands or
configuration requests.

Currently, the {\tt writelog} driver is capable of storing data from
the following interfaces: {\tt laser}, {\tt position}, {\tt wifi}.


\subsection*{Configuration file options}

\begin{center}
{\small \begin{tabularx}{\columnwidth}{|l|l|c|X|}
\hline
Name & Type & Default & Meaning\\
\hline
{\tt filename} & string & {\tt writelog.log} & Output log file name \\
{\tt devices} & list & none & A list of strings specifiying the
devices whose data should be stored.  Each device is specified as {\tt
``device:index''}. \\
\hline
\end{tabularx}}
\end{center}

%\subsection*{Notes}



\subsection*{Example: Storing Odometry and Laser Data}

The following configuration file will odometry from a Pioneer
and laser data from a SickLMS200 to a log file.
  \begin{verbatim}
  position:0 (driver "p2os_position")
  laser:0 (driver "sicklms200")
  null:0 
  (
    driver "writelog" 
    filename "foo.log" 
    devices ["position:0" "laser:0"]
    alwayson 1
  )
  \end{verbatim}
Note that the {\tt alwayson} flag will cause the driver to start
logging data as soon as Player is started, and will continue logging
data until Player is stopped.

Look in Section \ref{sect:readlog_driver} for an example that shows
how to replay this data using the {\tt readlog} driver.



